---
output:
  pdf_document: default
  html_document: default
---
```{r set-up, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      echo = TRUE, 
                      message = FALSE)
```

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(nycflights13)
```


### Question 1 (6 pts)

Refer to vectors x, y and z.

```{r}
x = c(1,9,6,7.8);y = c(8,2,NA,8.5);z = c(9,4,0,6.3)
```


(1) Use vectors x, y and z as columns to create a tibble 'df'. (2 pts)

(2) Find the min and max of each row, and add two columns called 'min' and 'max' to 'df'.  (2 pts)

(3) Add a column 'rank' to ‘df’ which ranks column 'z' ascendingly, and arrange the rows by 'rank'.  (2 pts)



#(1)


```{r}
df<- tribble(
  ~x,~y,~z,
  1,8,9,
  9,2,4,
  6,NA,0,
  7.8,8.5,6.3,
)
df
```

#(2) 


```{r}
df %>%
  mutate(min=pmin(x,y,z),
         max=pmax(x,y,z))

```

#(3)


```{r}

df%>% 
  mutate(rank=min_rank(z))%>%
  arrange(by=rank)
df
```

### Question 2 (7 points)

Refer to the 'flights' dataset.

(1) Find the 90th quantile of 'dep_delay' for flights per origin, and add a column 'q90'.  (2 pts)

(2) Find the standard deviation of 'dep_delay' for flights per origin, round to the first digits, and add a column 'sd'.  (2 pts)

(3) Find the 10th delay time for flights per origin, and add a column 'ten_th'.  (2 pts)

(4) Arrange the rows in a descending order of the column 'sd'.  (1 pt)







```{r}
flights%>%
  group_by(origin)%>%
  summarize(q90=quantile(dep_delay,0.9,na.rm=TRUE),
         sd=round(sd(dep_delay,na.rm=TRUE),  1),
         ten_th=nth(dep_delay,10))%>%
  arrange(by=desc(sd))


```



### Question 3 (2 pts)
Refer to 'df2'.

```{r}
df2 <- tibble(x =c("Mary\"ABBA", "Sam\"AAC", "Bill\"CD"))
df2
```
(1) Use 'separate_wider_delim', separate 'df2' into columns 'names' and 'grade'. (1 pt)

(2) Use 'separate_longer_position', separate column 'grade' into one letter grade per row. (1 pt)

```{r}
df2%>%
  separate_wider_delim (
    x,
    delim = "\""  ,
    names = c("name","grade")
    ) %>%
  separate_longer_position(grade,width=1)
```

