---
output:
  pdf_document: default
  html_document: default
---
```{r set-up, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      echo = TRUE, 
                      message = FALSE)
```


```{r load-packages, warning=FALSE, message=FALSE}
library(babynames)
library(tidyverse)
library(nycflights13)
head(babynames)
```


### Question 1 (6 pts)

Refer to the dataset 'babynames',

(1) Filter out names starting with 'A' or 'a' (2 pts)

(2) Create a new column 'Multiple', which returns true if there are consecutive 'n's (i.e., 'nn' or 'nnn', etc), and false otherwise. (2 pts).

(3) Create a new column 'Replacement', which replaces any sequence of consecutive 'n's in the name with a single '\.' (2 pts).

```{r}

babynames %>%
  filter(str_detect(name, "^[Aa]")) %>%
  mutate(Multiple=str_detect(str_to_lower(name),"n{2,}"),
         Replacemnt=str_replace_all(name,"n{2,}", '\\.'))
 
```


\newpage 

### Question 2 (8 points)

Refer to the 'flights' dataset, run the following code,

```{r}
make_datetime_100 <- function(year, month, day, time) {
  make_datetime(year, month, day, time %/% 100, time %% 100)
} 

flights_dt <- flights |> 
  filter(!is.na(dep_time), !is.na(arr_time)) |> 
  mutate(
    dep_time = make_datetime_100(year, month, day, dep_time),
    arr_time = make_datetime_100(year, month, day, arr_time),
  ) |> 
  select(tailnum, carrier, dep_time, arr_time)

```

(1) Return all flights which depart on January 1, 2013. (2 pts).

(2) Create new columns as 'n.dep_time' and 'n.arr_time', which returns a datetime which specifies the floor of the hour of departure / arrival respectively.  i.e., if departs at 5:54 PM on January 1, 2013, we want to return the date time corresponding to January 1, 2013 at 5:00 PM.  (2 pts)

(3) Create a column 'time_elapse.s' which calculates how long the flights fly in seconds (2 pts).

(4) Create a column 'time_elapse.h' which calculates how long the flights fly in hours (2 pts).

```{r}
flights_dt%>% filter(dep_time<ymd(20130102)) %>%
  mutate(n.dep_time=floor_date(dep_time,"hour"),
         n.arr_time= floor_date(arr_time,"hour"),
         time_elapse.s=(n.arr_time-n.dep_time),
         time_elapse.h= as.period(n.arr_time-n.dep_time))
```


\newpage 


### Question 3 (1 pts)
Refer to the 'flights' and 'weather' datasets, run the following code,

```{r}
flights2 <- flights %>%
  select(year, month,day, origin, dest, dep_time)%>%
  mutate(hour = dep_time%/%100)


```

Left join the column "temp" of "weather" to "flights 2", explicitly using the `by = ` argument so that you specify which keys you are joining on. 


```{r}
flights2%>% 
  left_join(weather%>%
              select(origin,year,month,day,hour,temp),join_by(origin,year,month,day,hour))
```
