---
output:
  pdf_document: default
  html_document: default
---
```{r set-up, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      echo = TRUE, 
                      message = FALSE)
```


```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(MASS)
library(ggthemes) 
```


 
### Question 1

Refer to the dataset 'iris',

(1) Use `str`, find the data types of variables in iris.

```{r}
iris%>%str
```


(2) Use `levels`, find the levels of 'Species' variable in iris.

```{r}
iris$Species%>%levels
```


(3) Fit a linear model 'm.full' of 'Sepal.Length' on all remaining variables and get the summary. 



```{r}
m.full <- lm(Sepal.Length ~ ., data=iris) 
summary(m.full)
```

(4) Use 'update' to do backward elimination.  Is there a smaller model with better adjusted R squared?  What is the final model after using backward elimination? 


```{r}
m.reduced <- step(m.full, direction="backward")
summary(m.reduced)
```


### Question 2

(1) Use `rnorm` to generate 100 samples from $$N(0,1)$$, and name it as 'sple'.


```{r}
sple = rnorm(100,0,1)
m = sple%>%mean() 
m
```


(2) Calculate the mean of 'sple', and name it as 'm'.



```{r}
sple = rnorm(100,0,1)
m = sple%>%mean() 
m
```



(3) Draw 100 bootstrap samples and calculate their means. Name the means as 'ms'.

(4) Use 'ggplot' to draw a histogram of 'ms'.

(5) Using these 100 bootstrap samples, provide an estimate for the 95% bootstrap confidence interval for the population mean.



```{r}
ms = numeric() 
for(i in 1:100){
ms[i] = sample(sple,100, replace = TRUE)%>%mean() }
ggplot(tibble(ms),aes(x=ms))+geom_histogram()
```



