---
title: "hw-6"
author: "Trisha Sharma"
date: "2023-12-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

PROBLEM 1



#a part



The tree heights follow normal distribution.
the parameters include:
-mean, mu = 100
-sd, standard deviation sigma = 25





#b part




```{r}
1- pnorm(25,mean=100,sd=25)
```





#c part




```{r}
pnorm(180,mean=100,sd=25) - pnorm(120,mean=100,sd=25)
```


 PROBLEM 2
 
 
 
 
#a part


Considering a random sample of normal distribution. The mean is 100 and the standard deviation is 20.
the first,second and third standard deviations from the mean and their values are as follows:

```{r}
sd1<-pnorm(120,100,20)-pnorm(80,100,20)
sd2<-pnorm(140,100,20)-pnorm(60,100,20)
sd3<-pnorm(160,100,20)-pnorm(40,100,20)
sd1
sd2
sd3
```



#b part



```{r}
sd68 <- 2*(pnorm(120,100,20))-1
sd95 <- 2*(pnorm(140,100,20))-1
sd99 <- 2*(pnorm(160,100,20))-1
sd68
sd95
sd99
```






PROBLEM 3



#a part


Y follows normal distribution.The mean and the standard deviation are as follows:
Since Y=1/2n(Xbar), 
         mean= mu/2
         variance= sigma^2/4n
         
         
         
         
         
         
#b part


According to the Central Limit Theorum, as n becomes large, the distribution of Xbar approaches a normal distribution.Since Xbar is normally distributed for a large n, Y will also be normally distributed.Thus, the mean and standard deviation of Y can be derived as follows:
E(Y) = mu/2
VAR(Y) = sigma^2/4n


PROBLEM 4
 


#a part


```{r}
org_dist<- 1- pnorm(180,150,30)
org_dist
standard_dist<- (180-150)/30
prob<- 1- pnorm(standard_dist)
prob
```

#b part 
For independent samples,the central limit theorum states that as the sample size increases the sample mean approaches normal distribution. The mean of the sample is aproximately equal to the population mean, whuch is, mu.The standard deviation is sigma/ underoot n. 



#c part


```{r}
sim_1000<- rnorm(1000,150,30)
mean(sim_1000)
```



#d part


```{r}
sim<- matrix(rnorm(1000 * 5000, 150, 30),ncol=5000)
mean1<- colMeans(sim)
final_mean<- mean(mean1)
std_dev<- sd(mean1)
final_mean
std_dev
```
The sample mean should be close to the population mean which is 150, and it turned out to be the expected mean. The standard deviation should be closer to 30/underoot 1000 (sigma/underoot n).


```{r}
sessionInfo()
```

