---
title: "lab-6"
author: "Trisha Sharma"
date: "2023-11-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Part 1

#a part


a) What is the probability that half the adults will like animal fries?
```{r}
dbinom(15,30,0.7)
```




#b

b) What is the probability that at least 2 adults will like animal fries?
```{r}
1-pbinom(1,30,0.7)
```

#c


c) What is the probability that between 5 and 20 adults will like animal fries?
```{r}
 pbinom(20, 30, 0.7) - pbinom(4, 30, 0.7)
```


#d

d) Simulate 1000 of these random variables. Create a histogram of this simulation. Explain why it
makes sense that the histogram’s highest peak occurs at a value around 21?


```{r}
random_var<-rbinom(1000,30,0.7)
hist(random_var)
```
The highest peak is around 21 as the probability of people liking animal fries is 70% of 30 people.If we calculate 0.3*0.7 we get the probability of 0.21.



#e



(e) Suppose that the number of people who like In n’ Out’s milkshakes in a given classroom is known
to follow a binomial distribution with n = 30 and p = 0.8. Let Y denote this random variable.
Find E(X + Y ).


E(X+Y)=E(X)+E(Y)

```{r}
E_X<- 0.7*30
E_Y<- 0.8*30
E_SUM<-E_X+E_Y
print(E_SUM)
```

Part 2


#a part


a) What is the expected number of people who will disappear yearly? What is the variance?

->  For Poisson distribution E(X) and VAR(X) are the same as the kniwn average rate(lambda).
therefore E(X)=30 and Var (X)=30.


#b part 


b) Find the probability that less than 10 people will disappear?
```{r}
ppois(10,30)-dpois(10,30)
```


#c part 


c) Suppose additionally, that the number of Eggo waffles stolen from a local grocery store (yearly),
is 200. Simulate 20 years’ worth of Eggo-waffle heists. Using R, find the proportion of years (in
the 20 simulated), in which the number of Eggo-waffles stolen was less than or equal to 80. Hint:
Use a logical comparison, and consider using the mean function.


```{r}
set.seed(35)
prop<-rpois(20,200)
prop_80<- mean(prop<= 80)
print(prop_80)

```

```{r}
sessionInfo()
```

