---
title: "LAB 5"
author: "Trisha Sharma"
date: "2024-02-13"
output: pdf_document
---

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(nycflights13)
library(ggthemes) 
```

```{r set-up, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      echo = TRUE, 
                      message = FALSE)
```
 

Refer to the dataset 'flights',

(1) Create a function 'filter_severe', which takes a dataset as an argument 'df' and returns a tibble which only keeps delayed flights (i.e., dep_delay > 0) but removes rows with missing values (2 pts).

(2) Use `across` to create a function 'grouped_mean', which takes a dataset as an argument 'df', also takes 'group_var' and 'mean_vars' as arguments, and returns a tibble which grouped by 'group_var', also calculates the mean of 'mean_vars' with missing values removed  and the number of flights. Also, name the summarized columns as "{.fn}\_for\_{.col}" and 'n' (3 pts).

(3) Apply 'filter_severe' and 'grouped_mean' to 'flights' data set sequentially. Let 'group_var' be origin, 'mean_vars' be 'dep_time' and 'air_time' (1 pt).

(4) Create a function 'hist', which takes a dataset as an argument 'df', in addition to the arguments 'x' and 'binwidth. The function returns a histogram of 'x' with the given binwidth using `geom_histogram` (2 pts).

(5) Create a function 'linearity_check', which takes a dataset as an argument 'df', two arguments 'x' and 'y'. The function returns a scatterplot between 'x' and 'y' with `geom_point()` and a line between 'x' and 'y' with `geom_smooth()` (2 pts).

(6) Apply 'filter_severe' to flights first, and apply 'hist' to the 'dep_time' column of 'flights' with binwidth as 1 (2 pts).

(7) Apply 'filter_severe' to flights first, and apply 'linearity_check' to the 'x' = 'air_time' and 'y' = 'dep_time' columns of 'flights' (2 pts).

(8) Fit a linear model of 'dep_time' given 'air_time' and check its summary (1 pt).




(1)
```{r}
filter_severe <- function(df) {df%>%
    filter(dep_delay>0)%>%
    drop_na()
}

```
(2)
```{r}
grouped_mean<- function(df,group_var,mean_vars) {
  df%>%
    group_by({{group_var}}) %>%
    summarise(n=n(),across({{mean_vars}},list(mean=\(x) mean(x,na.rm=TRUE)),
                           .names="{.fn}_for_{.col}"))
}
```
(3)
```{r}
flights%>%filter_severe()%>%grouped_mean(origin,c(dep_time,air_time))
```
(4)
```{r}
hist=function(df,x,binwidth){
  df%>%
    ggplot(aes(x={{x}}))+
    geom_histogram(binwidth=binwidth)
}
```
(5)
```{r}
linearity_check=function(df,x,y){
  df%>%
    ggplot(aes(x={{x}},y={{y}}))+
    geom_point()+
    geom_smooth()
}
```
(6)
```{r}
flights%>%filter_severe()%>%hist(dep_time,1)
```
(7)
```{r}
flights%>%filter_severe()%>%linearity_check(air_time,dep_time)
```
(8)
```{r}
lm(dep_time ~ air_time, data = flights %>% filter_severe()) %>%summary()
```
