---
title: "Tsharma_lab2"
author: "Trisha Sharma"
date: "2023-10-08"
output: pdf_document
---
PART 1
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```
The vector is as folows:
```{r}
myVec <- c(1,2,5,9,112)
print(myVec)
```
The mean of the elements of the myVec vector is:
```{r}
mean_myVec <- mean(myVec)
print(mean_myVec)
```
On subtracting elements 2 and 3 from myVec we get,
```{r}
Diff_myVec <- myVec[2]-myVec[3]
print(Diff_myVec)

```

The second vector created is as follows:
```{r}
myVec_new <- c(9,8,3,-1,111)
print(myVec_new)

```
The difference between myVec and myVec_new turns out to be :

```{r}
Diff_Vecs <- myVec-myVec_new
print(Diff_Vecs)

```
The standard deviation of the vectors :
```{r}
std_devi<- sd(Diff_Vecs)
print(std_devi)

```


```{r}
equal_8<- myVec != c(8,8,8,8,8)
print(equal_8)

```

PART 2
```{r}
data(trees) 
trees <- as.matrix(trees, dimnames = NULL)
```
#a 
The mean and the standard deviation,respectively:
```{r}
mean_values <- apply(trees,2,mean)
std_dev_values <- apply(trees, 2, sd)
print(mean_values)
print(std_dev_values)
```
#b
 3rd recorded cherry tree:
```{r}
trees[3,]
```
#c
```{r}
diameter <- trees[ ,1]
print(diameter)
```
Since 1 foot is equal to 12 inches, therefore to convert every element from inches to feet we divide every element by 12.
```{r}
diameter_feet <- diameter/12
print(diameter_feet)
```
#d
```{r}
new_matrix <- matrix(c(diameter_feet,trees[,2],ncol=2))
print(new_matrix)

```
The 3rd recorded cherry tree (row) from this matrix is:
```{r}
print(new_matrix[3,])
```

```{r}
sessionInfo()
```




